The natural history of scavenging in vertebrates

### 2016-03-07 natural history of scavenging.tex
Added quotes from Benbow

Our review is divided up into three sections, namely the land, air and sea. 
These are then subdivided into three geological eras the Cenozoic, Mesozoic and Palaeozoic. 
Each of these environments has a distinct phyiscal character that affects how a species forages for food which has obvious relevance for an animal searching for carrion.  
However, there is some commonality to a scavenger's environment and the problems in finding food that one would encounter. 
Notably, the resource environment of a scavenger is a patchily distributed one, because it is difficult to predict both when and where a carcass is produced. 
As a result of this, any animal existing as a scavenger must maximise its detection capabilities and minimise its locomotory costs \citep{ruxton2004obligate}.
Exploring which groups are likely to have moved towards these traits and thus existed as sccavengers over palaentological time forms the basis of this work.
%remember the journal is an ecological one at heart so I would always keep in mind about making it useful for ecologists over paelo people. In particular from the website "ECOGRAPHY publishes papers focused on broad spatial and temporal patterns, particularly studies of population and community ecology, macroecology, biogeography, and ecological conservation. Studies in ecological genetics and historical ecology are welcomed in the context of explaining contemporary ecological patterns".
"Interkingdom Competition among Vertebrates, Invertebrates, and Microbes"\citep{benbow2015introduction}
"For example, vertebrate scavengers appear to be disadvantaged when humidity and temperature favor microbial and invertebrate reproduction" \citep{benbow2015introduction}

@@

@@

"\cite{sazima1990necrofagia} predicted that  several components  of  snake  be-havior contribute to scavenging propensity. They  postulated  that  snakes  that  rely  on chemosensory information to acquire prey might forage  for  carrion  more  frequently than  those  whose  modes  of prey acquisition are driven by visual cues. Additionally, \cite{sazima1990necrofagia} suggested that habitat and diet preferences might be indicators of scavenging   propensity   be-cause  they  influence  the  likelihood of a particular species encountering carrion naturally. Based on these criteria, they pre-dicted that aquatic or semi-aquatic pisciv-orous snakes  would  scavenge  more  fre-quently than other species. Moreover, \cite{sazima1990necrofagia}  suggested that water currents that induce  aggrega-tions of carrion heighten the probability of carrion detection by these snakes (see also \cite{savitzky1992laboratory}).  Also,  chemical  gradients may  be  more  uniform  and  give  more  de-pendable  directional information in water \citep{sazima1990necrofagia}." \citep{devault2002scavenging}

"Investigations of ophidian metabolic re-quirements unveil additional advantages to carrion  utilization.  Snakes  exhibit  exceed-ingly  low  maintenance  metabolisms,  and most  can  survive  on  a  few  scant  feedings per year. It  is, therefore, possible for snakes to rely large-ly  on  infrequent,  less  energy-rich  meals. Carrion, which is by nature ephemeral and unpredictable, may represent such a food source  to  snakes.  Scavenging  might  allow snakes to meet their low metabolic needs more  easily  and  without  the  costs  associ-ated with subduing prey." \citep{devault2002scavenging}

>>>>

Our review is divided up into three sections, namely the land, air and sea. 
These are then subdivided into three geological eras the Cenozoic, Mesozoic and Palaeozoic. 
Each of these environments has a distinct phyiscal character that affects how a species forages for food which has obvious relevance for an animal searching for carrion.  
However, there is some commonality to a scavenger's environment and the problems in finding food that one would encounter. 
Notably, the resource environment of a scavenger is a patchily distributed one, because it is difficult to predict both when and where a carcass is produced. 
As a result of this, any animal existing as a scavenger must maximise its detection capabilities and minimise its locomotory costs \citep{ruxton2004obligate}.
Exploring which groups are likely to have moved towards these traits and thus existed as sccavengers over palaentological time forms the basis of this work.
%remember the journal is an ecological one at heart so I would always keep in mind about making it useful for ecologists over paelo people. In particular from the website "ECOGRAPHY publishes papers focused on broad spatial and temporal patterns, particularly studies of population and community ecology, macroecology, biogeography, and ecological conservation. Studies in ecological genetics and historical ecology are welcomed in the context of explaining contemporary ecological patterns".

%"Interkingdom Competition among Vertebrates, Invertebrates, and Microbes"\citep{benbow2015introduction}
%"For example, vertebrate scavengers appear to be disadvantaged when humidity and temperature favor microbial and invertebrate reproduction" \citep{benbow2015introduction}

%"However, in general, vertebrate scavenging represents the widest dispersal of nutrients and energy from carcasses as vertebrate movement scales away to the broader landscape" \citep{benbow2015introduction}

 %"Increased kill rates by top predators may represent a little acknowledged marginal cost to the vertebrate community, directly attributable to scavenging activity. Given the impor -tance of top-down effects in many ecosystems, even a minor alteration to predation rates as driven by vertebrate scavengers may cause a significant flux in community composition."\citep{benbow2015introduction}

 %"Cortés-Avizanda et al. (2009) found that the abundance of prey species (i.e., hares—Lepus spp. and squirrels—Sciurus  spp. in this case) decreased in sectors containing a carcass based on evidence from tracks in snow. An interesting hypothesis emerged, in which the scavengers that are recruited to a carcass may have temporarily played the dual role of increasing predator abundance near each carcass"\citep{benbow2015introduction}

%"Historically, the prevalence of scavenging activities has been greatly underestimated. However, upon recognition that (1) in most ecosystems, a large number of animals die from causes other than predation and thus become available to scavengers; (2) most carcasses are scavenged by vertebrates before they are completely decomposed by arthropods and bacteria; and (3) almost all carnivorous animals are facultative scavengers, the importance of scavenging in food webs seems unsurprising" \citep{benbow2015introduction}

%"This dispersion of carrion biomass by vertebrates is especially evident when carrion is initially concentrated spatially. For example, carcasses produced from fishing by-catch (Furness 2003), salmon (Salmonidae) die-offs (Hewson 1995), forest fires (Blanchard and Knight 1990), and single large carcasses (e.g., whales—Cetacea; Smith and Baco 2003) are often visited by multiple scavengers that range widely and therefore transport the nutrients from those carcasses over large distances."\citep{benbow2015introduction}

%"Cross-habitat nutrient transport can produce a variety of important outcomes in recipient systems (e.g., Polis et al. 2004), and scavengers can play a significant role in moving “ecologi -cal subsidies” between habitats. For example, the use of ocean-derived carrion by terrestrial mammals (Rose and Polis 1998) and birds (Schlacher et al. 2013) is extensive and may strongly influence dynamics of coastal food webs."\citep{benbow2015introduction}

% "Markandya et  al. (2008) estimated that the total costs to human health (including rabies cases from dog bites) that resulted from severe vulture declines totaled over $34 billion from 1993 to 2006. Also, Ogada et al. (2012) determined that the exclusion of vultures from large animal carcasses in Kenya resulted in a tripling of carcass decomposition times."\citep{benbow2015introduction}

% "Changes in global climate are also expected to substantially alter the availability of carrion resources in marine ecosystems as surface production of organic material could decline by 50% or more (Smith et al. 2008). Such a drastic reduction in productivity undoubtedly will impact a multitude of ecosystem processes, including the availability and distribution of carrion within marine ecosystems." \citep{benbow2015introduction}

@@

%"Of all the mammalian carnivores in Africa, brown, striped, and spotted hyenas (hereafter referred to simply as hyenas) derive the largest portion of their diet from scavenging. This is not surprising, as they show many unique adaptations specifically for scavenging. They have a unique body posture and a “rocking-horse” gait (Eloff 1964; Tilson and Henschel 1986; Hofer and East 1993a; Frank 1996) that allows them to cover long distances in search of carrion and prey."\citep{benbow2015introduction}

@@

%"\cite{sazima1990necrofagia} predicted that  several components  of  snake  be-havior contribute to scavenging propensity. They  postulated  that  snakes  that  rely  on chemosensory information to acquire prey might forage  for  carrion  more  frequently than  those  whose  modes  of prey acquisition are driven by visual cues. Additionally, \cite{sazima1990necrofagia} suggested that habitat and diet preferences might be indicators of scavenging   propensity   be-cause  they  influence  the  likelihood of a particular species encountering carrion naturally. Based on these criteria, they pre-dicted that aquatic or semi-aquatic pisciv-orous snakes  would  scavenge  more  fre-quently than other species. Moreover, \cite{sazima1990necrofagia}  suggested that water currents that induce  aggrega-tions of carrion heighten the probability of carrion detection by these snakes (see also \cite{savitzky1992laboratory}).  Also,  chemical  gradients may  be  more  uniform  and  give  more  de-pendable  directional information in water \citep{sazima1990necrofagia}." \citep{devault2002scavenging}

%"Investigations of ophidian metabolic re-quirements unveil additional advantages to carrion  utilization.  Snakes  exhibit  exceed-ingly  low  maintenance  metabolisms,  and most  can  survive  on  a  few  scant  feedings per year. It  is, therefore, possible for snakes to rely large-ly  on  infrequent,  less  energy-rich  meals. Carrion, which is by nature ephemeral and unpredictable, may represent such a food source  to  snakes.  Scavenging  might  allow snakes to meet their low metabolic needs more  easily  and  without  the  costs  associ-ated with subduing prey." \citep{devault2002scavenging}
